Projecting genetic associations through gene expression patterns highlights disease etiology and drug mechanisms

### 2023-08-03 output/latex/manuscript.tex
latex: reformat author list

\begin{itemize}
\item
  \textbf{Milton Pividori}\textsuperscript{1,2}
\item
  \textbf{Sumei Lu}\textsuperscript{3}
\item
  \textbf{Binglan Li}\textsuperscript{4}
\item
  \textbf{Chun Su}\textsuperscript{3}
\item
  \textbf{Matthew E. Johnson}\textsuperscript{3}
\item
  \textbf{Wei-Qi Wei}\textsuperscript{5}
\item
  \textbf{Qiping Feng}\textsuperscript{5}
\item
  \textbf{Bahram Namjou}\textsuperscript{6}
\item
  \textbf{Krzysztof Kiryluk}\textsuperscript{7}
\item
  \textbf{Iftikhar Kullo}\textsuperscript{8}
\item
  \textbf{Yuan Luo}\textsuperscript{9}
\item
  \textbf{Blair D. Sullivan}\textsuperscript{10}
\item
  \textbf{Benjamin F. Voight}\textsuperscript{11,12,13}
\item
  \textbf{Carsten Skarke}\textsuperscript{13}
\item
  \textbf{Marylyn D. Ritchie}\textsuperscript{1}
\item
  \textbf{Struan F.A. Grant}\textsuperscript{3,14,15,1}
\item
  \textbf{Casey S. Greene}~\textsuperscript{\protect\hyperlink{correspondence}{\Letter}} \textsuperscript{16,2}
\end{itemize}

>>>>

Milton Pividori\textsuperscript{1,2},
Sumei Lu\textsuperscript{3},
Binglan Li\textsuperscript{4},
Chun Su\textsuperscript{3},
Matthew E. Johnson\textsuperscript{3},
Wei-Qi Wei\textsuperscript{5},
Qiping Feng\textsuperscript{5},
Bahram Namjou\textsuperscript{6},
Krzysztof Kiryluk\textsuperscript{7},
Iftikhar Kullo\textsuperscript{8},
Yuan Luo\textsuperscript{9},
Blair D. Sullivan\textsuperscript{10},
Benjamin F. Voight\textsuperscript{11,12,13},
Carsten Skarke\textsuperscript{13},
Marylyn D. Ritchie\textsuperscript{1},
Struan F.A. Grant\textsuperscript{3,14,15,1},
Casey S. Greene~\textsuperscript{\protect\hyperlink{correspondence}{\Letter}} \textsuperscript{16,2}
